---
title: "The Great British Bake Off, Series `r params$series`"
params:
  color:
    label: 'Fill color (hex):'
    value: '#17a2b8'
  colorpop:
    label: 'Pop-out color (hex):'
    value: '#e7553c'
  series:
    input: numeric
    label: 'Series:'
    max: 9
    min: 1
    step: 1
    value: 1
output:
  html_document:
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
fig_path <- glue::glue("figs/series-{params$series}/")
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      message = FALSE,
                      fig.path = fig_path)
library(tidyverse)
library(here)
library(glue)
library(wesanderson)
theme_set(theme_minimal())
```

```{r import-tidy, include=FALSE}
ratings <- readr::read_csv(here::here("data/ratings.csv"))
```

```{r selected-series, include=FALSE}
this_ratings <- ratings %>% 
  filter(series == params$series)

all_ratings <- ratings %>% 
  filter(!series == params$series) %>% 
  add_count(episode) %>% 
  group_by(episode, n) %>% 
  summarize(median_viewers = median(viewers_7day))

median_viewers <- ratings %>% 
  summarize(median_viewers = median(viewers_7day)) %>% 
  pull()

median_series <- this_ratings %>%
  summarize(median_viewers = median(viewers_7day)) %>% 
  pull()
```


# Overview

\

Series `r params$series` premiered on `r min(this_ratings$uk_airdate)`, and had `r n_distinct(this_ratings$episode)` episodes.

\

# Ratings

\

Figure \@ref(fig:ratings-by-episode) shows the 7-day viewers (in millions) by episode.

\

```{r ratings-by-episode, fig.cap="Viewers by episode"}
ggplot(this_ratings, 
       aes(as.factor(episode), viewers_7day, group = 1)
       ) + 
  geom_point(colour = params$color) + 
  geom_line(colour = params$color) + 
  labs(
    x = "Episode", 
    y = "Viewers (millions)"
  ) +
  expand_limits(y = 0) 
```

\

# Finale

\

The series `r params$series` finale aired on on `r max(this_ratings$uk_airdate)`. On average, finales always garner more viewers than premieres.

\

```{r finale-viewers, fig.cap="Finale 7-day Viewers, Relative to Premiere"}
# some more serious wrangling here
first_last <- ratings %>% 
  select(series, episode, viewers_7day) %>% 
  group_by(series) %>% 
  filter(episode == 1 | episode == max(episode)) %>% 
  mutate(episode = recode(episode, `1` = "first", .default = "last")) 

viewers_wide <- first_last %>%
  pivot_wider(names_from = episode, values_from = viewers_7day) %>%
  mutate(finale_bump = last - first,
         pct_change = (last - first) / first)
  
ggplot(viewers_wide, 
       aes(x = fct_rev(as.factor(series)),
           y = finale_bump)) +
  geom_col(data = filter(viewers_wide, !series == params$series), 
           fill = params$color, 
           alpha = .5) +
  geom_col(data = filter(viewers_wide, series == params$series), 
           fill = params$colorpop, 
           alpha = .5) +
  coord_flip() +
  labs(x = "Series", y = "Difference in Viewers- Finale vs Premiere (millions)") 
```

\

Figure \@ref(fig:finale-viewers) shows the "bump" observed in numbers of viewers for the finale compared to the premiere. The percentage difference may be more meaningful, here however, as shown in Figure \@ref(fig:finale-percent).

\

```{r finale-percent, fig.cap="Percent Increases in Viewers"}
ggplot(viewers_wide, aes(x = fct_rev(as.factor(series)),
                      y = pct_change)) +
  geom_point(color = params$color, size = 2) +
  geom_segment(aes(xend = fct_rev(as.factor(series)), yend = 0), 
               color = params$color) +
  geom_text(aes(label = scales::percent(pct_change)), hjust = -.25) +
  labs(x = "Series", y = "% Change in Viewers from First to Last Episode") +
  scale_y_continuous(labels = scales::percent, limits = c(0, .85)) +
  coord_flip()
```

\

```{r finale-scatterplot}
ggplot(viewers_wide, aes(x = first, y = last)) +
  geom_point(data = filter(viewers_wide, !series == params$series)) +
  geom_point(data = filter(viewers_wide, series == params$series), 
             colour = params$colorpop) +
  geom_smooth(se = FALSE, color = params$color) +
  geom_abline(slope = 1, intercept = 0, color = "gray", alpha = .5) +
  geom_text(aes(label = series), hjust = -1) +
  labs(x = "Premiere Episode 7-day Viewers (millions)",
       y = "Finale Episode 7-day Viewers (millions)") +
  coord_equal(ratio = 1)
```

